Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/intro.tex
Edit contributions in intro

With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data capture \cite{denning2014situ}, but human attention is a finite resource \cite{bohme2011security}. Therefore, user concerns should be investigated to warn users only about situations they are likely to care about. Informed, select notifications make for a better user experience and prevents habituation to such notifications while avoiding scandalous breaches of privacy.

The goal of this paper is to gain a better sense of user concerns for wearables. To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices. We surveyed 1,784 Internet users for their perceptions of wearable devices and contribute the following: \\[-0.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Comparisons of users' perceptions of a range of privacy and security risks of wearables. We found that users care much more about the type of data than the recipient of the data.
\item Insight into how users feel about various data recipients. We observed that users make less distinction between sharing data with friends, co-workers, and the general public, comparatively to sharing with an application's servers.
\item A report and categorization of users' self-reported top concerns for wearable devices. We give an sense of what broad concerns users have, which can be used to guide research in unexplored use cases. 
\item Rankings of how data-collection capabilities of wearable devices compared to more familiar technologies.  Most saw new capabilities as benign, but we suspect that this may be due to a lack of exposure to these newer technologies.
\end{itemize}

>>>>

With the additional capabilities of wearable devices and their increasing popularity, people have expressed interest in being notified before data is captured \cite{denning2014situ}. However, human attention is a finite resource \cite{bohme2011security}, and bombarding users with notifications is likely to be counter-productive as it can lead to user frustration and habituation. Therefore, user concerns need to be investigated so that systems can warn users only about situations they are likely to care about.

The goal of this paper is to gain a better sense of user concerns about wearables. To our knowledge, this is the first large-scale study to investigate user security and privacy concerns for wearable devices. We surveyed 1,784 Internet users about their perceptions of wearable devices and contribute the following: \\[-0.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We compare users' perceptions of a range of privacy and security risks of wearables. We found that user concern is driven more by the type of data being captured than the recipient of the data.
\item Our results shed light into how users feel about various data recipients. We observed that users make less distinction between sharing data with friends, co-workers, and the general public, compared to sharing with an application's servers.
\item We analyze users' self-reported top concerns regarding wearable devices. The results give an sense of what broad concerns users have, which can be used to guide future research in unexplored use cases. 
\item We examine how serious users perceive the risks of wearables to be, compared to risks associated with more familiar technologies. Most of our participants saw wearables' new capabilities as benign, though we suspect that this could be due to a lack of exposure to these newer technologies.
\end{itemize}
